---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  font-family: Arial, sans-serif;
  background: linear-gradient(to right, #eef2f3, #ffffff);
  color: #333;
  margin: 20px;
}

h2 {
  color: #2c7fb8;
  border-bottom: 2px solid #2c7fb8;
  padding-bottom: 5px;
}

img {
  display: block;
  margin: 20px auto;
  max-width: 90%;
}
```

## 📱 Social Media Video Engagement Analysis

This report analyses social media video data to explore how engagement varies across different types of content and video characteristics.

---

## 📊 Key Summary Insights

```{r}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS3D0vho-JD4mG1pKYAzq4H99lq0HDVjgWKD98vFDYk6qrdazM_NmNIqFtmHIh45-cFUqXFPhr6yWha/pub?gid=1423379554&single=true&output=csv"

data <- read_csv(csv_url)

data <- data %>%
  rename(
    content_type = `What type of content is this?`,
    video_length = `How long was the video? (in seconds)`,
    engagement   = `How engaging was the video?`
  )

avg_engagement <- mean(data$engagement, na.rm = TRUE)
mean_length <- mean(data$video_length, na.rm = TRUE)
total_responses <- nrow(data)

summary_text <- paste(
  "The average engagement score is", round(avg_engagement, 2), 
  ". The average video length is", round(mean_length, 1), "seconds.",
  "There are", total_responses, "observations in this dataset."
)

summary_text
```

---

## 📈 Engagement Distribution

This chart shows how engagement scores are distributed across all observed videos.

```{r}
ggplot(data, aes(x = factor(engagement), fill = factor(engagement))) +
  geom_bar() +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(
    x = "Engagement Score (1–5)",
    y = "Count",
    title = "Distribution of Engagement Scores"
  )
```

---

## 🎥 Content Type Distribution

This chart shows the frequency of different content types in the dataset.

```{r}
ggplot(data, aes(y = content_type, fill = content_type)) +
  geom_bar() +
  theme_minimal() +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Content Type",
    title = "Content Type Distribution"
  )
```

---

## 🔍 Dynamic Insights

```{r}
high_engagement <- sum(data$engagement >= 4, na.rm = TRUE)

insight_text <- paste(
  "A total of", high_engagement, "videos had high engagement (scores of 4 or 5).",
  "This suggests that a noticeable proportion of content performs well."
)

insight_text
```