---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  font-family: Arial, sans-serif;
  background: linear-gradient(to right, #eef2f3, #ffffff);
  color: #333;
  margin: 20px;
}

h2 {
  color: #2c7fb8;
  border-bottom: 2px solid #2c7fb8;
  padding-bottom: 5px;
}

ul {
  background: white;
  padding: 15px;
  border-radius: 10px;
  list-style-type: none;
}

img {
  display: block;
  margin: 20px auto;
  max-width: 90%;
  border-radius: 10px;
}
```

## 📱 Social Media Video Engagement Analysis

This report explores how different types of social media content perform based on user engagement and video characteristics.  
The dataset includes observations of video type, length, and engagement ratings.

---

## 📊 Key Summary Insights

```{r}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS3D0vho-JD4mG1pKYAzq4H99lq0HDVjgWKD98vFDYk6qrdazM_NmNIqFtmHIh45-cFUqXFPhr6yWha/pub?gid=1423379554&single=true&output=csv"
data <- read_csv(csv_url)

data <- data %>%
  rename(
    content_type = `What type of content is this?`,
    video_length = `How long was the video? (in seconds)`,
    engagement   = `How engaging was the video?`
  )

avg_engagement <- mean(data$engagement, na.rm = TRUE)
mean_length <- mean(data$video_length, na.rm = TRUE)
total_responses <- nrow(data)

cat("<ul>")
cat(paste("<li><b>Average engagement score:</b>", round(avg_engagement, 2), "</li>"))
cat(paste("<li><b>Average video length:</b>", round(mean_length, 1), "seconds</li>"))
cat(paste("<li><b>Total observations:</b>", total_responses, "</li>"))
cat("</ul>")
```

---

## 📈 Engagement Distribution

This chart shows how engagement scores are distributed across all observed videos.

```{r}
print(
  ggplot(data, aes(x = factor(engagement), fill = factor(engagement))) +
    geom_bar() +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(
      x = "Engagement Score (1–5)",
      y = "Count",
      title = "Distribution of Engagement Scores"
    )
)
```

---

## 🎥 Content Type Comparison

This chart highlights which types of content appear most frequently in the dataset.

```{r}
print(
  ggplot(data, aes(y = content_type, fill = content_type)) +
    geom_bar() +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(
      x = "Count",
      y = "Content Type",
      title = "Content Type Distribution"
    )
)
```

---

## 🔍 Dynamic Insights

```{r}
high_engagement_pct <- mean(data$engagement >= 4, na.rm = TRUE) * 100

cat(paste(
  "On average, videos received an engagement score of",
  round(avg_engagement, 2),
  ". Approximately",
  round(high_engagement_pct, 1),
  "% of videos achieved high engagement (scores of 4 or 5)."
))
```